### 2017-11-16 paper/mechanism.tex
backup

Listing 1 shows the three stages of a generalized graph vertex processing model - \textit{Assign}, \textit{Process} and \textit{Apply}, given a graph \textit{G}, some vertex properties \textit{P} and an iteration count \textit{N}. The \textit{Assign} stage generates an input vector \textit{x} using the vertex properties \textit{P}. The \textit{Process} stage applies the input vector \textit{x} to the graph \textit{G} and generates an output vector \textit{y}. The\textit{ Apply} gather the resulting output vector to update the vertex properties for the next iteration. The graph program executes the three stages for several iterations until it converges. A direct mapping of our incoming edges algorithm to this processing model is also provided in Listing 1, where the identity vector is used for the vector properties. The \textit{Assign} and \textit{Apply} stages of this program are simple identity operators, while the \textit{Process} stage perform a matrix-vector multiplication. The input graph can be represented as a sparse matrix and the computation done using a Sparse Matrix-Sparse Vector Multiplication (SpMSpV) kernel which can be accelerated on multi-core CPUs \cite{GraphMat} or on GPUs \cite{MapGraph}. FlexGraph's objective is to provide a more energy efficient graph processing backend using a FPGA for hardware acceleration \cite{Catapult}.

@@

With the rising adoption of FPGAs in production data centers \cite{Catapult}, there is a need to increase its ecosystem by making them more energy efficient as well as accessible to both the users and designers. Modern CPU-FPGA platforms \cite{CPU-FPGA} provide tightly-coupled shared-memory CPU-FPGA integration \cite{CAPI} \cite{CCI}, making then easier to program and efficient for hardware acceleration. Figure \ref{fig:harp_arch} shows an overview architecture of the Intel Xeon-FPGA platform prototype that we used in our evaluation. It has a dual-socket system, one containing a 10-core Intel Xeon E5-2680 CPU and the other containing an Altera Stratix V 5SGXEA FPGA operating at 200 MHz. The two sockets are connected via a 6.4 GT/s QPI \cite{QPI} link for data transfer. The FPGA's area is partitioned into two main blocks - the Application Function Unit (AFU) or 'Green' bitstream allocated for the custom accelerator and the 'Blue' bitstream implementing the Cache Coherent Interface (CCI) for the accelerator. The CCI runtime implements address translation (1024 page table entries) with request re-ordering for a total of 2 GB of addressable memory. The AFU memory interface is 64-byte cache-line addressable and it is up to the accelerator to extend the memory interface if fine grained (e.g. single byte) access is desired.

@@

>>>>

Listing 1 shows the three stages of a generalized graph vertex processing model - \textit{Assign}, \textit{Process} and \textit{Apply}, given a graph \textit{G}, some vertex properties \textit{P} and an iteration count \textit{N}. The \textit{Assign} stage generates an input vector \textit{x} using the vertex properties \textit{P}. The \textit{Process} stage applies the input vector \textit{x} to the graph \textit{G} and generates an output vector \textit{y}. The\textit{ Apply} gather the resulting output vector to update the vertex properties for the next iteration. The graph program executes the three stages for several iterations until it converges. A direct mapping of our incoming edges algorithm to this processing model is also provided in Listing 1, where the identity vector is used for the vector properties. The \textit{Assign} and \textit{Apply} stages of this program are simple identity operators, while the \textit{Process} stage perform a matrix-vector multiplication. The input graph can be represented as a compressed sparse matrix to only store the non-zero entries of the graph. This data structure enables accelerated computation, often using a Sparse Matrix-Sparse Vector Multiplication (SpMSpV) kernel to target multi-core CPUs \cite{GraphMat} or GPUs \cite{MapGraph}. The computation that cannot be accelerated is simply executed on the general-purpose host CPU. FlexGraph's objective is to provide a more energy efficient graph processing backend using a FPGA for hardware acceleration \cite{Catapult}.

@@

\begin{figure*}
\centering
\begin{subfigure}{0.4\textwidth}
    \includegraphics[width=\textwidth]{figures/offload_model}
    \caption{Offload model}
    \label{fig:offload_model}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
    \includegraphics[width=\textwidth]{figures/collaborative_model}
    \caption{Collaborative model}
    \label{fig:collaborative_model}
\end{subfigure}
\caption{Shared Memory Compute Models}
\label{fig:compute_model}
\end{figure*}

With the rising adoption of FPGAs in production data centers \cite{Catapult}, there is a need to increase its ecosystem by making them more energy efficient as well as accessible to both the users and designers. Modern CPU-FPGA platforms \cite{CPU-FPGA} provide tightly-coupled shared-memory CPU-FPGA integration \cite{CAPI} \cite{CCI}, making then easier to program and efficient for hardware acceleration. Figure \ref{fig:harp_arch} shows an overview architecture of the Intel Xeon-FPGA platform prototype that we used in our evaluation. It has a dual-socket system, one containing a 10-core Intel Xeon E5-2680 CPU and the other containing an Altera Stratix V 5SGXEA FPGA operating at 200 MHz. The two sockets are connected via a 6.4 GT/s QPI \cite{QPI} link for data transfer. The FPGA's area is partitioned into two main blocks - the Application Function Unit (AFU) or 'Green' bitstream allocated for the custom accelerator and the 'Blue' bitstream implementing the Cache Coherent Interface (CCI) for the accelerator. The CCI runtime implements a 64 KB direct-mapped cache to support address translation (1024 page table entries) with request re-ordering for a total of 2 GB of addressable memory. The AFU memory interface is 64-byte cache-line addressable and it is up to the accelerator to extend the interface if fine grained (e.g. single byte) access is desired.

@@

The prevalent execution model for accelerator design is the offload model \cite{Accelerators} where computation takes place on discrete copies of a shared resource that are optimized for efficient access by the target device. In this model of computation, the host processor applies some layout translation on the data before making it available to the client accelerator (see Figure \ref{fig:offload_model}). The additional latency of the translation process is generally mitigated using optimization techniques such as batching and double-buffering. The offload model is well suited for discrete memory systems where the necessary data transfer can be coupled with layout translation. One attractive application of shared-memory systems is the enabling of efficient collaborative computation (see Figure \ref{fig:collaborative_model}) in which all attached compute elements can access the same shared resource and modifying it during the course of the program execution. It is particularly ideal if the data layout provides efficient access by the compute devices. Contrarily to existing Graph Analytics Accelerators \cite{Graphicionado} \cite{GraphOps} that employ a custom optimized graph data structure for computation, Flexgraph uses a sparse matrix format for computation. This decision provides several advantages - first, it is storage efficient because the graph's physical memory is shared - second, it enables collaborative computation with the host CPU, leveraging the large ecosystem of matrix-based frameworks \cite{CombBlas} \cite{Pegasus} - third, it decouples the software and hardware design, enabling them to scale independently.
